### 2013-08-14 main.tex
put family in aknowledgements
make tables more consistent

Last but not least I am greatful to Anna M\uller for her support, encouragement and company
Thank you for giving me the strength needed for this endeavour.

>>>>

I also thank my parents and my sister for their continuing support.

Last but not least I am greatful to Anna M\"uller for her support, encouragement and company
Thank you for giving me the strength needed for this endeavour.

### 2013-08-14 mil/paper.tex
make tables more consistent

\section{Theoretical settings}\seclabel{intro}
Multiple instance learning is a supervised learning scenario first proposed by \citet{dietterich1997solving}.
In multiple instance learning, examples are multi sets of instances, called bags, and each bag is assigned a class label.
It is assumed that each instance has a true label, defined by an underlying concept. The label of a bag is positive, if and only if one of
the instances it contains is labeled positive. The true label of instances is assumed to be unobserved by the learner who only has access to bag labels.

@@

\section{Related Work}
The theoretical analysis of multiple instance learning started with \citet{auer1997approximating} and later \citet{blum1998note}.
These works assume that instances are drawn i.i.d.\ from a single distribution over instances. Blum and Kalai showed that in this
setting, if the underlying concept is PAC-learnable in polynomial time, then the multiple instance learning problem is PAC-learnable
in polynomial time. Auer et\,al.\ showed that if there is an algorithm to PAC-learn multiple instance learning with axis-parallel
rectangles that is polynomial in size of the bag and dimension of the instance features, then it is possible to polynomially
PAC-learn DNF-formulars, a problem that is solvable only if $\text{RP}=\text{NP}$.
Recently, \citet{sabato2009homogeneous,DBLP:journals/corr/abs-1107-2021} proved bounds on the VC dimension and
fat shattering dimension of multiple instance learners by the corresponding dimension for a base learner.

@@

\section{Preliminaries}
Throughout this work, $\mathcal{X}$ denotes the space of all instances. Bags are multi sets of instance $X=\{x_1,\dotsc, x_r\}$.
As usual in supervised learning tasks, we assume our training examples ($X_i,Y_i)$ to be i.i.d.\ from an unknown distribution.
We denote the label of an instance $x_i$ by $y_i$ and the label of the bag $X_i$ as $Y_i = \max\{y_j | x_j \in  X_i\}$.
We assume the bag size $r\in \mathbb{N}$ to be constant over all bags in a given problem. This restriction simplifies the treatment
significantly while our results can in great parts be carried over to settings with varying bag sizes.
We consider arbitrary classifiers $h_I\colon \mathcal{X} \rightarrow \{0, 1\}$ with associated bag classifier
$h_B(X) = \max \{h(x_1),\dotsc,h(x_r)\}$.
The goal is to learn a classifier $h$ which minimizes expected instance misclassification, given training bags and bag labels
$X_i$ and $Y_i$.
We do not consider specific hypotheses classes but instead try to bound the expected error of $h$ using the expected error of $h_B$.
During all of this work, we assume that the true instance labels are never observed.
We use the following notation: $p(h_I(x)=0):= h_0$, the negative rate of the classifier,
$p(h_I(x) \neq y) := e_I$, the instance error, and $p(h_B(X) \neq Y) := e_B$, the bag error.

\section{Necessary Assumptions}\seclabel{assumptions}
If we allow instances inside bags and their labels to have arbitrary dependencies, we are trying to find
$y_1,\dotsc,y_r$ maximizing $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)$. This is a structured 
prediction problem for which there is no hope solving it, given only bag labels.
Therefore, as usual in multiple instance learning, we assume there is an underlying concept for instances,
i.\,e.\ the label of each instance depends only on this instance.
In other words, we assume $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)=p(y_1|x_1) \cdot p(y_r|x_r)$.

@@

\section{Independent Case}\seclabel{iid}
The simplest case in which learning instance prediction is possible is the case when instances are globally i.i.d.,
i.\,e.\ when instances inside a bag are independent of each other. This is a very strong assumption that might be
violated in practical applications. On the other hand, strong results can be proved in this setting.

@@

\section{Restricted Dependent Case}
As remarked in \Secref{assumptions}, it is not possible to bound the instance classification error
when allowing arbitrary dependencies between instances. On the other hand, the i.i.d.\ assumption of \Secref{iid}
might be too strong in a practical setting.
Therefore, we propose an assumption that is both very general and allows learning of instance classification:
We assume that each bag has a ``hidden cause'' $Z$, conditioned on which all instances are independent.
More formally, we assume
\begin{align}
    p(x_1,\dotsc,x_r)=\int_Z p(x_1)\cdot \dotsc \cdot p(x_r) dZ.
\end{align}
The intuition behind this assumption is as follows. In the classical case of drug activity prediction~\citep{dietterich1997solving}, a bag corresponds
to a molecule and each instance corresponds to a different geometric configurations. These are certainly not independent.
If one knew the ``true'' geometric characteristics of the molecule, each configuration could be derived from that.

>>>>

\section{Theoretical Analysis of Instance Level Prediction}\seclabel{intro}
%TODO clean up
Multiple instance learning is a supervised learning scenario first proposed by \citet{dietterich1997solving}.
In multiple instance learning, examples are multi sets of instances, called bags, and each bag is assigned a class label.
It is assumed that each instance has a true label, defined by an underlying concept. The label of a bag is positive, if and only if one of
the instances it contains is labeled positive. The true label of instances is assumed to be unobserved by the learner who only has access to bag labels.

@@

\subsection{Previous Analysis}
The theoretical analysis of multiple instance learning started with \citet{auer1997approximating} and later \citet{blum1998note}.
These works assume that instances are drawn i.i.d.\ from a single distribution over instances. Blum and Kalai showed that in this
setting, if the underlying concept is PAC-learnable in polynomial time, then the multiple instance learning problem is PAC-learnable
in polynomial time. Auer et\,al.\ showed that if there is an algorithm to PAC-learn multiple instance learning with axis-parallel
rectangles that is polynomial in size of the bag and dimension of the instance features, then it is possible to polynomially
PAC-learn DNF-formulars, a problem that is solvable only if $\text{RP}=\text{NP}$.
Recently, \citet{sabato2009homogeneous,DBLP:journals/corr/abs-1107-2021} proved bounds on the VC dimension and
fat shattering dimension of multiple instance learners by the corresponding dimension for a base learner.

@@

\subsection{Preliminaries}
Throughout this work, $\mathcal{X}$ denotes the space of all instances. Bags are multi sets of instance $X=\{x_1,\dotsc, x_r\}$.
As usual in supervised learning tasks, we assume our training examples ($X_i,Y_i)$ to be i.i.d.\ from an unknown distribution.
We denote the label of an instance $x_i$ by $y_i$ and the label of the bag $X_i$ as $Y_i = \max\{y_j | x_j \in  X_i\}$.
We assume the bag size $r\in \mathbb{N}$ to be constant over all bags in a given problem. This restriction simplifies the treatment
significantly while our results can in great parts be carried over to settings with varying bag sizes.
We consider arbitrary classifiers $h_I\colon \mathcal{X} \rightarrow \{0, 1\}$ with associated bag classifier
$h_B(X) = \max \{h(x_1),\dotsc,h(x_r)\}$.
The goal is to learn a classifier $h$ which minimizes expected instance misclassification, given training bags and bag labels
$X_i$ and $Y_i$.
We do not consider specific hypotheses classes but instead try to bound the expected error of $h$ using the expected error of $h_B$.
During all of this work, we assume that the true instance labels are never observed.
We use the following notation: $p(h_I(x)=0):= h_0$, the negative rate of the classifier,
$p(h_I(x) \neq y) := e_I$, the instance error, and $p(h_B(X) \neq Y) := e_B$, the bag error.

\subsection{Necessary Assumptions}\seclabel{assumptions}
If we allow instances inside bags and their labels to have arbitrary dependencies, we are trying to find
$y_1,\dotsc,y_r$ maximizing $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)$. This is a structured 
prediction problem for which there is no hope solving it, given only bag labels.
Therefore, as usual in multiple instance learning, we assume there is an underlying concept for instances,
i.\,e.\ the label of each instance depends only on this instance.
In other words, we assume $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)=p(y_1|x_1) \cdot p(y_r|x_r)$.

@@

\subsection{Independent Case}\seclabel{iid}
The simplest case in which learning instance prediction is possible is the case when instances are globally i.i.d.,
i.\,e.\ when instances inside a bag are independent of each other. This is a very strong assumption that might be
violated in practical applications. On the other hand, strong results can be proved in this setting.

@@

\subsection{Restricted Dependent Case}
As remarked in \Secref{assumptions}, it is not possible to bound the instance classification error
when allowing arbitrary dependencies between instances. On the other hand, the i.i.d.\ assumption of \Secref{iid}
might be too strong in a practical setting.
Therefore, we propose an assumption that is both very general and allows learning of instance classification:
We assume that each bag has a ``hidden cause'' $Z$, conditioned on which all instances are independent.
More formally, we assume
\begin{align}
    p(x_1,\dotsc,x_r)=\int_Z p(x_1)\cdot \dotsc \cdot p(x_r) dZ.
\end{align}
The intuition behind this assumption is as follows. In the classical case of drug activity prediction~\citep{dietterich1997solving}, a bag corresponds
to a molecule and each instance corresponds to a different geometric configurations. These are certainly not independent.
If one knew the ``true'' geometric characteristics of the molecule, each configuration could be derived from that.
